Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-14 snapshot_system/arch.tex
update graph
update eval

@@

While we can use the standard mark-and-sweep technique~\cite{mark-sweep}, 
it still takes significant time to conduct this process every time there is a snapshot deletion.
In the case of Alibaba, snapshot backup is conducted automatically and there are 
about 10 snapshot stored for every user. When there is
a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
a balanced storage use. Given the large number of snapshot deletion requests, we seek
a fast solution with a very low resource usage to delete snapshots.

@@

\item {\bf Approximate deletion with fast summary comparison.}
Then when there is a snapshot deletion,  
we need to identify if  chunks to be deleted from one snapshot
are still used by other snapshots. 
This is done approximately and quickly by comparing the reference pointers of deleted snapshots with
the merged reference bloom-filter summary of other live snapshots.
The merging of live snapshot bloom-filter bits uses the logical OR operator and the merged vector still takes $z$ bits.
Since the number of live snapshots is limited for each VM (e.g. 10 in the Alibaba's production system), 
the time cost of this comparison is small.
%Instead of scanning the entire append store indices, we merge the type-1 summaries of all
%valid snapshots. 
%Since each VM has uniform bloom filter parameters to create snapshot summaries, 
%such merged summeries give us a compact representation of
%all block fingerprints that are still in use.
%Thus by the property of bloom filter, if a fingerprint is not found in merged summaries, 
%we are certain that block is no longer used by any valid snapshot, it would be then added
%to append store's deletion log.
However, there is a small false-positive ratio which
would identify unused data as in use, resulting in temporary storage leakage.

@@

When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we need to execute a leak repair:
\[
\frac{L}{U} = \frac{R \Delta u \epsilon}{u+(h-1)\Delta u } > \tau 
\Longrightarrow R > \frac{\tau}{\epsilon}\frac{u + (h-1)\Delta u}{\Delta u}
\]
For example in our tested dataset,  
each VM keeps $h=10$ snapshots and each snapshot has
about 1-5\% of new data. Thus $\frac{\Delta u}{u}=0.05$ at most. With 40GB snapshot size, $u\approx = 10$ millions.
Then $U=10.45$ millions.
We choose  $\epsilon = 0.01$ and $\tau=0.1$. Then from the bloom filter  false positive formula, 
$z=10U=100.45$ million bits. $R=290$.
Then we would expect leak repair be triggered once for 
every 290 runs of approximate deletion. 
When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
only one full leak repair for one VM scheduled for every 12 days. Each repairs uses about 90MB memory on average
as discussed earlier and takes a short period of time.
% which is sufficiently small to offset the heavy I/O workload of the mark-sweep process.

>>>>

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/deletion.png, width=3.5in}
  \caption{Approximate deletion}
  \label{fig:deletion_flow}
\end{figure}

@@

While we can use the mark-and-sweep technique~\cite{Guo2011}, 
it still takes significant time to conduct this process every time there is a snapshot deletion.
In the case of Alibaba, snapshot backup is conducted automatically and there are 
about 10 snapshot stored for every user. When there is
a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
a balanced storage use. Given the large number of snapshot deletion requests, we seek
a fast solution with a very low resource usage to delete snapshots.

@@

\item {\bf Approximate deletion with fast summary comparison.}
When there is a snapshot deletion,  
we need to identify if  chunks to be deleted from that snapshot
are still used by other snapshots. 
This is done approximately and quickly by comparing the 
reference pointers of deleted snapshot with
the merged reference bloom-filter summary of other live snapshots.
The merging of live snapshot bloom-filter bits uses the logical OR operator 
and the merged vector still takes $z$ bits.
Since the number of live snapshots is limited for 
each VM (e.g. 10 in the Alibaba's production system), 
the time cost of this comparison is small.
%Instead of scanning the entire append store indices, we merge the type-1 summaries of all
%valid snapshots. 
%Since each VM has uniform bloom filter parameters to create snapshot summaries, 
%such merged summeries give us a compact representation of
%all block fingerprints that are still in use.
%Thus by the property of bloom filter, if a fingerprint is not found in merged summaries, 
%we are certain that block is no longer used by any valid snapshot, it would be then added
%to append store's deletion log.

If a chunk's reference pointer is not found in the merged summary vector, we are sure that
this chunk is not used by any live snapshots, thus it's safe delete it. 
However, among all the chunks that suppose to be deleted, 
there is a small false-positive ratio which
would identify unused chunks as in use, resulting in temporary storage leakage.

@@

When leakage ratio $L/U$ exceeds a pre-defined threshold $\tau$, we need to execute a leak repair:
\[
\frac{L}{U} = \frac{R \Delta u \epsilon}{u+(h-1)\Delta u } > \tau 
\Longrightarrow R > \frac{\tau}{\epsilon}\times\frac{u + (h-1)\Delta u}{\Delta u}
\]
For example in our tested dataset,  
each VM keeps $h=10$ snapshots and each snapshot has
about 1-5\% of new data. Thus $\frac{\Delta u}{u}=0.05$ at most. With 40GB snapshot size, $u\approx = 10$ millions.
Then $U=10.45$ millions.
We choose  $\epsilon = 0.01$ and $\tau=0.1$. Then from the bloom filter  false positive formula, 
$z=10U=100.45$ million bits. $R=290$.
Then we would expect leak repair be triggered once for 
every 290 runs of approximate deletion. 
When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
only one full leak repair for one VM scheduled for every 12 days. Each repairs uses about 90MB memory on average
as discussed earlier and takes a short period of time.
% which is sufficiently small to offset the heavy I/O workload of the mark-sweep process.

### 2013-08-14 snapshot_system/eval1.tex
update eval

\subsection{Resource Usage}
{\bf Storage cost of replication.}
\begin{table}
    \begin{tabular}{|c|c|}
    \hline
    PDS replication degree & Total space (GB) \\ \hline
    3                      & 3065             \\ \hline
    4                      & 3072             \\ \hline
    5                      & 3079             \\ \hline
    6                      & 3086             \\ \hline
    7                      & 3093             \\ \hline
    \end{tabular}
\caption{Storage space cost under different PDS replication degree}
\label{tab:replication_cost}
\end{table}

Table~\ref{tab:replication_cost} shows the total storage space required by VC as the PDS replication degree is changed. The increase in storage cost is minimal because the PDS makes up a very small percent of the total storage space, but the increase in reliability can be much more significant (see Figure~\ref{fig:pds-replication}).

\begin{table}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    Tasks & CPU & Mem (MB) & Disk W (MB/s) & Network \\ \hline
    1                      & 19\% & 18.1 & 32.1     &    \\ \hline
    2                      & 35\% & 31.8 & 53     &    \\ \hline
    4                      & 63\% & 54.1 & 84     &    \\ \hline
    6                      & 77\% & 71.9  & 88.5   &     \\ \hline
    8                      & 82\% & 90.5   & 89.2   &    \\ \hline
    10                      & 85\% & 97.2   & 90.4   &    \\ \hline
    12                      & 91\% & 95.6    & 91.5   &   \\ \hline
    \end{tabular}
\caption{Resource usage under concurrent backup tasks}
\label{tab:resource_usage}
\end{table}

@@

>>>>

\subsection{Resource Usage}
\begin{table}
    \begin{tabular}{|c|c|}
    \hline
    PDS replication degree & Total space (GB) \\ \hline
    3                      & 3065             \\ \hline
    4                      & 3072             \\ \hline
    5                      & 3079             \\ \hline
    6                      & 3086             \\ \hline
    7                      & 3093             \\ \hline
    \end{tabular}
\caption{Storage space cost under different PDS replication degree}
\label{tab:replication_cost}
\end{table}

{\bf Storage cost of replication.} Table ~\ref{tab:replication_cost} shows the total storage space required by VC as the PDS replication degree is changed. The increase in storage cost is minimal because the PDS makes up a very small percent of the total storage space, but the increase in reliability can be much more significant (see Figure~\ref{fig:pds-replication}).

\begin{table}
    \begin{tabular}{|c|c|c|c|}
    \hline
    Tasks & CPU & Mem (MB) & Disk W (MB/s) \\ \hline
    1     & 19\% & 18.1 & 32.1 \\ \hline
    2     & 35\% & 31.8 & 53 \\ \hline
    4     & 63\% & 54.1 & 84 \\ \hline
    6     & 77\% & 71.9 & 88.5 \\ \hline
    8     & 82\% & 90.5 & 89.2 \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\caption{Resource usage of concurrent backup tasks in each node}
\label{tab:resource_usage}
\end{table}

{\bf Resource usage and its impact to cluster} We further studied the resource usage when running concurrent snapshot backup tasks on each node. 
Table ~\ref{tab:resource_usage} gives the CPU, memory and disk write workload of running different number of backup tasks at the same time. 
Notice that memory and CPU used by PDS index and QFS are not included since they belong to the cloud infrastructure services and are shared among many applications.
We see our hybrid deduplication scheme only occupies small amount of system resources in general, the memory usage is especially small because
our efficient localized deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in memory for duplicate detection.

@@

Base on the observed performance numbers, even with a single backup task per node and enforcing the disk read speed to
50 MB/s,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
 at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.
